Simulating the Lipkin-Meshov-Glikov model on a classical computer

### 2023-05-29 doc/paper.tex
Describing qubits and quantum gates
Signed-off-by: Gregz9 <gregorkajda@gmail.com>

>>>>

 \section{Method}

 \subsection{Quantum gates}
 The main difference between clasical computers and their quantum counterpart lays in the underlying data they process. While a classical computer operates on binary digits (bits), which represent low and high voltage levels, a qunatum computer operates directly on particles such as atoms. These leads to different ways of handling the data, as the properties of atoms and the physical theorems that describe their behavior do not allows us to process them in a way identical to how a classical computer processes bits

On a classical machine, data is represented using classical bits and processed using logical gates such as \emph{and, or, xor} and \emph{nand}. On a quantum computer, data is represented using \emph{qubits} which are a digital representation of particles. The main difference between classical computers and quantum computers lays namely in what data each of these technological wonders operate on. T
